Plot Figures for McDuffie et al., 2023 (those generated in R)

### 2023-05-23 analysis/Manuscript/Paper_RFigures.Rmd
Manuscript figure updates prior to submission

```{r libraries, include = FALSE}
library('tidyverse')
library('reshape2')
library('patchwork')
library('RColorBrewer')
library('maps')
library('mapproj')
library('arrow')
library('readxl')
library('zoo')
```

@@

#specify input and output paths
Plots <-file.path(getwd(),'analysis','Manuscript','Plots')
Input <- file.path(getwd(),'analysis','Manuscript','BenMAP','Inputs')

@@

#Read in RFF-SP data
# Pre-processed in /code/1_build_inputs_for_momm_rft.R
rffsp <- read_parquet(file.path(Inputs_socio, 'rffsp_pop_gdp_all_trials.parquet'))

@@

#plot line graph of global total and top 10 countries (for MMM)
Plots <- file.path(getwd(),'analysis','Manuscript','Plots')
input <- file.path(getwd(),'analysis','Manuscript','BenMAP','Outputs')

@@

@@

country_total <- countryResults %>%
  select(c('COUNTRY','Region','SuperRegion','Model','TotalResults','TotalPct2_5','TotalPct97_5')) %>%
  filter(Model == MODEL) %>%
  rename(region = COUNTRY) #%>%

# load map data and align country names
worldData <- map_data("world")
#correct region names
worldData["region"][worldData["region"] == "Russia"] <- "Russian Federation"
worldData["region"][worldData["region"] == "USA"] <- "United States"
worldData["region"][worldData["region"] == "Virgin Islands" & worldData['subregion']==' US'] <- "US Virgin Islands"
worldData["region"][worldData["region"] == "Taiwan"] <- "China, Taiwan Province of China"
worldData["region"][worldData["region"] == "Trinidad" | worldData['region']=='Tobago'] <- "Trinidad and Tobago"
worldData["region"][worldData["region"] == "Grenadines"| worldData['region']=='Saint Vincent'] <- "Saint Vincent and the Grenadines"
worldData["region"][worldData["region"] == "Swaziland"] <- "Eswatini"
worldData["region"][worldData["region"] == "UK"] <- "United Kingdom"
worldData["region"][worldData["region"] == "Cape Verde"] <- "Cabo Verde"
worldData["region"][worldData["region"] == "Republic of Congo"] <- "Congo"
worldData["region"][worldData["region"] == "Democratic Republic of the Congo"] <- "Congo DRC"
worldData["region"][worldData["region"] == "Ivory Coast"] <- "Cote d'Ivoire"
worldData["region"][worldData["region"] == "Brunei"] <- "Brunei Darussalam"
worldData["region"][worldData["region"] == "Antigua"| worldData['region']=='Barbuda'] <- "Antigua and Barbuda"
worldData["region"][worldData["region"] == "Palestine"] <- "Palestinian Territory"
worldData["region"][worldData["region"] == "China" & worldData['subregion']=='Hong Kong'] <- "China, Hong Kong SAR"
worldData["region"][worldData["region"] == "China" & worldData['subregion']=='Macao'] <- "China, Macao SAR"
worldData["region"][worldData["region"] == "Guernsey"| worldData['region']=='Jersey'] <- "Channel Islands"

#Merge data
MergedData <- left_join(worldData, country_total, by = 'region')
#replace zero with na
MergedData$TotalResults[MergedData$TotalResults ==0] <- NA

#chloropleth of world
p5 <- ggplot() +
  geom_polygon(data = MergedData, aes(x=long, y = lat, group=group, fill = TotalResults),
               color = 'black',linewidth=0.15)+
  scale_fill_fermenter("Total Deaths",
                       n.breaks=9,
                        type = 'seq',
                       direction = -1,
                        palette = "Spectral",
                        na.value='lightgray',
                       limits=c(0,100000),
                       breaks= c(0,100,1000,10000,100000),
                       label=scales::comma)+
  theme_void()+
  theme(legend.spacing.y = unit(.5,'cm'),
        legend.text = element_text(size=12),
        legend.title = element_text(size=13))+

  guides(col = guide_legend(override.aes = list(shape = 15, size = 10)))+
  coord_map(projection = 'mercator',xlim=c(-180,180),ylim = c(-55,80))

@@

Plots <- file.path(getwd(), 'analysis','Manuscript','Plots')
input <- file.path(getwd(),'input')
countryResults <- read.csv(paste0(input,'/BenMAP',"/Country Results Summary by Model & Year.csv"))

@@

#read in population
socio_inputs <- file.path('input','RFF','lookup_tables')
mean.pop<-read.csv(file.path(socio_inputs,"rff_pop_means.csv")) #this data set includes all countries (rff-sp does not)
mean.pop <- mean.pop %>%
  filter(Year ==2020) %>%
  mutate(mean_pop = mean_pop *1000) %>% #convert to ppl counts
  group_by(LocID) %>%
  summarise_at(.vars = c('mean_pop'), sum)

@@

# read in map data and align country names
worldData <- map_data("world")
#correct region names
worldData["region"][worldData["region"] == "Russia"] <- "Russian Federation"
worldData["region"][worldData["region"] == "USA"] <- "United States"
worldData["region"][worldData["region"] == "Virgin Islands" & worldData['subregion']==' US'] <- "US Virgin Islands"
worldData["region"][worldData["region"] == "Taiwan"] <- "China, Taiwan Province of China"
worldData["region"][worldData["region"] == "Trinidad" | worldData['region']=='Tobago'] <- "Trinidad and Tobago"
worldData["region"][worldData["region"] == "Grenadines"| worldData['region']=='Saint Vincent'] <- "Saint Vincent and the Grenadines"
worldData["region"][worldData["region"] == "Swaziland"] <- "Eswatini"
worldData["region"][worldData["region"] == "UK"] <- "United Kingdom"
worldData["region"][worldData["region"] == "Cape Verde"] <- "Cabo Verde"
worldData["region"][worldData["region"] == "Republic of Congo"] <- "Congo"
worldData["region"][worldData["region"] == "Democratic Republic of the Congo"] <- "Congo DRC"
worldData["region"][worldData["region"] == "Ivory Coast"] <- "Cote d'Ivoire"
worldData["region"][worldData["region"] == "Brunei"] <- "Brunei Darussalam"
worldData["region"][worldData["region"] == "Antigua"| worldData['region']=='Barbuda'] <- "Antigua and Barbuda"
worldData["region"][worldData["region"] == "Palestine"] <- "Palestinian Territory"
worldData["region"][worldData["region"] == "China" & worldData['subregion']=='Hong Kong'] <- "China, Hong Kong SAR"
worldData["region"][worldData["region"] == "China" & worldData['subregion']=='Macao'] <- "China, Macao SAR"
worldData["region"][worldData["region"] == "Guernsey"| worldData['region']=='Jersey'] <- "Channel Islands"

#Merge data
MergedData <- left_join(worldData, country_plot, by = 'region')
#replace zero with na
MergedData$death_percap[MergedData$death_percap ==0] <- NA
MergedData$AvgResponse[MergedData$AvgResponse ==0] <- NA
MergedData$MeanMortalityRate[MergedData$MeanMortalityRate ==0] <- NA
MergedData <- MergedData %>%
  mutate(rel_death_percap = death_percap/mean(death_percap, na.rm=TRUE),
         rel_AvgResponse = AvgResponse/mean(AvgResponse, na.rm=TRUE),
         rel_mean_pop = mean_pop/mean(mean_pop, na.rm=TRUE),
         rel_MeanMortalityRate = MeanMortalityRate/mean(MeanMortalityRate, na.rm=TRUE))

#chloropleth of world Per capita deaths
p5 <- ggplot() +
  geom_polygon(data = MergedData, aes(x=long, y = lat, group=group, fill = death_percap),
               color = 'black',linewidth=0.15)+
  scale_fill_fermenter("Deaths Per Capita",
                       n.breaks=10.5,
                        type = 'seq',
                       direction = -1,
                        palette = "Spectral",
                        na.value='lightgray',
                       #values=rescale(c(-1,0,1)),
                       limits=c(#0,
                                min(MergedData$death_percap, na.rm=TRUE),
                                0.3),
                       labels = c('Minimum',rep('',8),'Maximum'))+
  theme_void()+
  theme(legend.position = 'right')+
  theme(legend.key.height = unit(0.5,'cm'),
        legend.spacing.y = unit(.5,'cm'),
        legend.text = element_text(size=12),
        legend.title = element_text(size=13))+
  guides(col = guide_legend(override.aes = list(shape = 15, size = 10)))+
  coord_map(projection = 'mercator',xlim=c(-180,180),ylim = c(-55,80))

p5

#mortality rate
p6 <- ggplot() +
  geom_polygon(data = MergedData, aes(x=long, y = lat, group=group, 
                                      fill = MeanMortalityRate),
               color = 'black',linewidth=0.15)+
  scale_fill_fermenter("Respiratory Mortality Rates",
                       n.breaks=9,
                        type = 'seq',
                       direction = -1,
                        palette = "Spectral",
                        na.value='lightgray',
                       limits=c(min(MergedData$MeanMortalityRate, na.rm=TRUE),
                                max(MergedData$MeanMortalityRate, na.rm=TRUE)),
                       labels = c('Minimum','','','','','','Maximum'))+

  theme_void()+
  ggtitle("b) Respiratory Mortality Rates Per 100K")+
  theme(legend.position = 'none')+
  theme(legend.spacing.y = unit(.5,'cm'),
        legend.text = element_text(size=12),
        legend.title = element_text(size=13))+
  theme(plot.title = element_text(size = 20))+
  guides(col = guide_legend(override.aes = list(shape = 15, size = 10)))+
  coord_map(projection = 'mercator',xlim=c(-180,180),ylim = c(-55,80))
p6

#population
p7 <- ggplot() +
  geom_polygon(data = MergedData, aes(x=long, y = lat, group=group, fill = mean_pop),
               color = 'black',linewidth=0.15)+
  scale_fill_fermenter("Population",
                       n.breaks=9,
                        type = 'seq',
                       direction = -1,
                        palette = "Spectral",
                        na.value='lightgray',
                       limits=c(min(MergedData$mean_pop, na.rm=TRUE),
                                max(MergedData$mean_pop, na.rm=TRUE)),
                       #breaks= c(0,100,1000,5000,10000,20000,40000,60000,100000),
                       #breaks= c(0,100,1000,10000,100000),
                       #n.breaks = 6,
                       #label=scales::comma)+
                       labels = c('Minimum','','','','','','Maximum'))+
  theme_void()+
  ggtitle('a) Population')+
  theme(legend.position = 'none')+
  theme(legend.spacing.y = unit(.5,'cm'),
        legend.text = element_text(size=12),
        legend.title = element_text(size=13))+
  theme(plot.title = element_text(size = 20))+
  guides(col = guide_legend(override.aes = list(shape = 15, size = 10)))+
  coord_map(projection = 'mercator',xlim=c(-180,180),ylim = c(-55,80))
p7

#avg response
p8 <- ggplot() +
  geom_polygon(data = MergedData, aes(x=long, y = lat, group=group, fill = AvgResponse),
               color = 'black',linewidth=0.15)+
  scale_fill_fermenter("",
                       n.breaks=9,
                        type = 'seq',
                       direction = -1,
                        palette = "Spectral",
                        na.value='lightgray',
                       limits=c(min(MergedData$AvgResponse, na.rm=TRUE),
                                max(MergedData$AvgResponse, na.rm=TRUE)),
                       labels = c('Minimum','','','','','','Maximum'))+
  theme_void()+
  ggtitle(expression(paste('c) Average Ozone Response (pptv ', O[3],"/", "ppbv ",CH[4],')')))+
  theme(legend.position = 'bottom')+
  theme(legend.key.width = unit(2,'cm'),
        legend.text = element_text(size=12),
        legend.title = element_text(size=13))+
  theme(plot.title = element_text(size = 20))+
  coord_map(projection = 'mercator',xlim=c(-180,180),ylim = c(-55,80))
p8

@@

Plots <- file.path(getwd(), 'analysis','Manuscript','Plots')
inputs <- file.path(getwd(),'analysis','Manuscript','BenMAP','Outputs')
countryresults <-
   read_csv(file.path(inputs,"npd_country_damage_transformation_woutCessation.csv"),
           col_types = cols())

@@

## function for labels
means = cResultslong %>% 
  group_by_at(c('discount.rate','SuperRegion')) %>% 
  summarise(means=mean) %>% 
  ungroup() %>%
  mutate(across(c('means'), ~ signif(.,3)))

lower = cResultslong %>% 
  group_by_at(c('discount.rate','SuperRegion')) %>% 
  summarise(means=`2.5%`) %>% 
  ungroup() %>%
  mutate(across(c('means'), ~ signif(.,3)))

upper = cResultslong %>% 
  group_by_at(c('discount.rate','SuperRegion')) %>% 
  summarise(means=`97.5%`) %>% 
  ungroup() %>%
  mutate(across(c('means'), ~ signif(.,3)))

@@

#Read in 
Plots <- file.path(getwd(), 'analysis','Manuscript','Plots')
inputs <- file.path(getwd(),'analysis','Manuscript','BenMAP','Outputs')
rft_inputs <- file.path(getwd(),'output','npd')

@@

p1 <- plot_data %>%
  mutate(subgroup_col = (fct_relevel(subgroup_col, '3.0% CDR',
                                     "2.0% CDR","3.0% Ramsey",
                                     "2.5% Ramsey","1.5% Ramsey",
                                     "MIROC","GISS","GFDL",
                                     "CESM2","HadGEM",
                                     '-50% NOx','+50% NOx',
                                     "SocioEcon. Lower","SocioEcon. Upper",
                                     "CRF Lower","CRF Upper"
                                     ))) %>%
  ggplot( aes(x=(subgroup_col), y=(val_col),fill=group_col))+
  geom_bar(stat='identity',width = 0.4)+
  #scale_fill_brewer() (palette = 'Spectral',direction=-1)+
  scale_fill_manual(name = '',values=c(brewer.pal(11,"Spectral")[c(2,4,8,10,11)]),
  breaks= c('CRF (95% CI)','Socioeconomics (95% CI)','NOx Emissions (\u0394 50%)','GCM (mean)','Discount Rate (mean)'))+
  coord_flip()+
  theme_minimal()+
  xlab('')+
  ylab("Change in Global $1660(2020)/mT" ~CH[4])+
  theme(axis.text = element_text(size=16),
        axis.title = element_text(size=16))+
  scale_y_continuous(limits = c(-1000, 1300),label = scales::dollar)+
  theme(legend.position = c(0.8,0.25),
        legend.title=element_text(size=14), 
        legend.text=element_text(size=14))

>>>>

```{r libraries, include = FALSE}
library('tidyverse')
library('reshape2')
library('patchwork')
library('RColorBrewer')
#library('maps')
#library('mapproj')
library('arrow')
library('readxl')
library('zoo')
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
```

@@

#specify input and output paths
dir.root <- getwd()
Plots <-file.path('../..','analysis','Manuscript','Plots')
Input <- file.path('../..','analysis','Manuscript','BenMAP','Inputs')

@@

#Read in RFF-SP data
# Pre-processed in /code/1_build_inputs_for_momm_rft.R
rffsp <- read_parquet(file.path(getwd(),Inputs_socio, 'rffsp_pop_gdp_all_trials.parquet'))

@@

#plot line graph of global total and top 10 countries (for MMM)
Plots <- file.path('../..','analysis','Manuscript','Plots')
input <- file.path('../..','analysis','Manuscript','BenMAP','Outputs')

@@

#map of country mortality results
MODEL = 'GFDL'

@@

country_total <- countryResults %>%
  select(c('COUNTRY','Region','SuperRegion','Model','TotalResults','TotalPct2_5','TotalPct97_5')) %>%
  filter(Model == MODEL) %>%
  rename(region = COUNTRY) #%>%
country_total["region"][country_total["region"] == "Cote d'Ivoire"] <- "Côte d'Ivoire"
country_total["region"][country_total["region"] == "Congo DRC"] <- "Democratic Republic of the Congo"
country_total["region"][country_total["region"] == "Congo"] <- "Republic of Congo"
country_total["region"][country_total["region"] == "Cabo Verde"] <- "Cape Verde"
country_total["region"][country_total["region"] == "Gambia"] <- "The Gambia"
country_total["region"][country_total["region"] == "China, Hong Kong SAR"] <- "Hong Kong"
country_total["region"][country_total["region"] == "South Korea"] <- "Republic of Korea"
country_total["region"][country_total["region"] == "Laos"] <- "Lao PDR"
country_total["region"][country_total["region"] == "China, Macao SAR"] <- "Macao" 
country_total["region"][country_total["region"] == "Sao Tome and Principe"] <- "	São Tomé and Principe"
country_total["region"][country_total["region"] == "North Korea"] <- "Dem. Rep. Korea"
country_total["region"][country_total["region"] == "Palestinian Territory"] <- "Palestine"
country_total["region"][country_total["region"] == "Eswatini"] <- "Swaziland"
country_total["region"][country_total["region"] == "China, Taiwan Province of China"] <- "Taiwan"

# # load map data and align country names
# worldData <- map_data("world")
# #correct region names
# worldData["region"][worldData["region"] == "Russia"] <- "Russian Federation"
# worldData["region"][worldData["region"] == "USA"] <- "United States"
# worldData["region"][worldData["region"] == "Virgin Islands" & worldData['subregion']==' US'] <- "US Virgin Islands"
# worldData["region"][worldData["region"] == "Taiwan"] <- "China, Taiwan Province of China"
# worldData["region"][worldData["region"] == "Trinidad" | worldData['region']=='Tobago'] <- "Trinidad and Tobago"
# worldData["region"][worldData["region"] == "Grenadines"| worldData['region']=='Saint Vincent'] <- "Saint Vincent and the Grenadines"
# worldData["region"][worldData["region"] == "Swaziland"] <- "Eswatini"
# worldData["region"][worldData["region"] == "UK"] <- "United Kingdom"
# worldData["region"][worldData["region"] == "Cape Verde"] <- "Cabo Verde"
# worldData["region"][worldData["region"] == "Republic of Congo"] <- "Congo"
# worldData["region"][worldData["region"] == "Democratic Republic of the Congo"] <- "Congo DRC"
# worldData["region"][worldData["region"] == "Ivory Coast"] <- "Cote d'Ivoire"
# worldData["region"][worldData["region"] == "Brunei"] <- "Brunei Darussalam"
# worldData["region"][worldData["region"] == "Antigua"| worldData['region']=='Barbuda'] <- "Antigua and Barbuda"
# worldData["region"][worldData["region"] == "Palestine"] <- "Palestinian Territory"
# worldData["region"][worldData["region"] == "China" & worldData['subregion']=='Hong Kong'] <- "China, Hong Kong SAR"
# worldData["region"][worldData["region"] == "China" & worldData['subregion']=='Macao'] <- "China, Macao SAR"
# worldData["region"][worldData["region"] == "Guernsey"| worldData['region']=='Jersey'] <- "Channel Islands"
# MergedData <- left_join(worldData, country_total, by = 'region')

world <- ne_countries(scale = "medium", returnclass = "sf")
world <- world %>% 
  filter(sov_a3 != 'ATA') #%>% #remove antarctica
  #select(-c("formal_en","formal_fr","note_adm0","note_brk","name_sort","name_alt"))
  #select("name_long")

MergedData <- left_join(world, country_total, by = c('name_long'='region'))
#replace zero with na
MergedData$TotalResults[MergedData$TotalResults ==0] <- NA

#chloropleth of world
p5 <- ggplot() +
  #geom_polygon(data = MergedData, aes(x=long, y = lat, group=group, fill = TotalResults),
  #             color = 'black',linewidth=0.15)+
  geom_sf(data = MergedData, color = "black",  aes(fill = TotalResults))+
  coord_sf(crs = "+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 
           +datum=WGS84 +units=m +no_defs")+
  scale_fill_fermenter("Total Deaths",
                       n.breaks=9,
                        type = 'seq',
                       direction = -1,
                        palette = "Spectral",
                        na.value='lightgray',
                       limits=c(0,100000),
                       breaks= c(0,100,1000,10000,100000),
                       label=scales::comma)+
  theme_bw()+
  theme(legend.spacing.y = unit(.5,'cm'),
        legend.text = element_text(size=12),
        legend.title = element_text(size=13))+
  theme(panel.border = element_rect(color = "transparent"),
        axis.text.x= element_blank(),
        axis.ticks.x = element_blank())+
  #theme(panel.grid.major = element_line(color = 'gray75', 
  #                                      linetype = "solid",
  #                                      linewidth = 0.25),
  #      panel.grid.minor = element_line(color = 'gray75', 
  #                                      linetype = "solid",
  #                                      linewidth = 0.25),
  #      panel.grid = element_line(colour = "grey70", size=2),
  #      )+

  guides(col = guide_legend(override.aes = list(shape = 15, size = 10)))#+
  #coord_proj("+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")
  #coord_map(projection = 'mercator',xlim=c(-180,180),ylim = c(-55,80))

@@

Plots <- file.path( 'analysis','Manuscript','Plots')
input <- file.path('../..','input')

countryResults <- read.csv(file.path(input,'BenMAP',"Country Results Summary by Model & Year.csv"))

@@

#read in population
socio_inputs <- file.path('../..','input','RFF','lookup_tables')
mean.pop<-read.csv(file.path(socio_inputs,"rff_pop_means.csv")) #this data set includes all countries (rff-sp does not)
mean.pop <- mean.pop %>%
  filter(Year ==2020) %>%
  mutate(mean_pop = mean_pop *1000) %>% #convert to ppl counts
  group_by(LocID) %>%
  summarise_at(.vars = c('mean_pop'), sum)

@@

country_plot["region"][country_plot["region"] == "Cote d'Ivoire"] <- "Côte d'Ivoire"
country_plot["region"][country_plot["region"] == "Congo DRC"] <- "Democratic Republic of the Congo"
country_plot["region"][country_plot["region"] == "Congo"] <- "Republic of Congo"
country_plot["region"][country_plot["region"] == "Cabo Verde"] <- "Cape Verde"
country_plot["region"][country_plot["region"] == "Gambia"] <- "The Gambia"
country_plot["region"][country_plot["region"] == "China, Hong Kong SAR"] <- "Hong Kong"
country_plot["region"][country_plot["region"] == "South Korea"] <- "Republic of Korea"
country_plot["region"][country_plot["region"] == "Laos"] <- "Lao PDR"
country_plot["region"][country_plot["region"] == "China, Macao SAR"] <- "Macao" 
country_plot["region"][country_plot["region"] == "Sao Tome and Principe"] <- "	São Tomé and Principe"
country_plot["region"][country_plot["region"] == "North Korea"] <- "Dem. Rep. Korea"
country_plot["region"][country_plot["region"] == "Palestinian Territory"] <- "Palestine"
country_plot["region"][country_plot["region"] == "Eswatini"] <- "Swaziland"
country_plot["region"][country_plot["region"] == "China, Taiwan Province of China"] <- "Taiwan"

# # load map data and align country names
world <- ne_countries(scale = "medium", returnclass = "sf")
world <- world %>% 
  filter(sov_a3 != 'ATA') #%>% #remove antarctica
  #select(-c("formal_en","formal_fr","note_adm0","note_brk","name_sort","name_alt"))
  #select("name_long")

MergedData <- left_join(world, country_plot, by = c('name_long'='region'))
#replace zero with na
MergedData$death_percap[MergedData$death_percap ==0] <- NA
MergedData$AvgResponse[MergedData$AvgResponse ==0] <- NA
MergedData$MeanMortalityRate[MergedData$MeanMortalityRate ==0] <- NA
MergedData <- MergedData %>%
  mutate(rel_death_percap = death_percap/mean(death_percap, na.rm=TRUE),
         rel_AvgResponse = AvgResponse/mean(AvgResponse, na.rm=TRUE),
         rel_mean_pop = mean_pop/mean(mean_pop, na.rm=TRUE),
         rel_MeanMortalityRate = MeanMortalityRate/mean(MeanMortalityRate, na.rm=TRUE))

#chloropleth of world Per capita deaths
p5 <- ggplot() +
  geom_sf(data = MergedData, color = "black",  aes(fill = death_percap))+
  coord_sf(crs = "+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 
           +datum=WGS84 +units=m +no_defs")+
  scale_fill_fermenter("Deaths Per Capita",
                       n.breaks=10.5,
                        type = 'seq',
                       direction = -1,
                        palette = "Spectral",
                        na.value='lightgray',
                       limits=c(#0,
                                min(MergedData$death_percap, na.rm=TRUE),
                                0.3),
                       labels = c('Minimum',rep('',8),'Maximum'))+
  theme_bw()+
  theme(legend.position = 'right')+
  theme(legend.key.height = unit(0.5,'cm'),
        legend.spacing.y = unit(.5,'cm'),
        legend.text = element_text(size=12),
        legend.title = element_text(size=13))+
  theme(panel.border = element_rect(color = "transparent"),
        axis.text.x= element_blank(),
        axis.ticks.x = element_blank())+
  guides(col = guide_legend(override.aes = list(shape = 15, size = 10)))#+
p5

#mortality rate
p6 <- ggplot() +
  geom_sf(data = MergedData, color = "black",  aes(fill = MeanMortalityRate))+
  coord_sf(crs = "+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 
           +datum=WGS84 +units=m +no_defs")+
  scale_fill_fermenter("Respiratory Mortality Rates",
                       n.breaks=9,
                        type = 'seq',
                       direction = -1,
                        palette = "Spectral",
                        na.value='lightgray',
                       limits=c(min(MergedData$MeanMortalityRate, na.rm=TRUE),
                                max(MergedData$MeanMortalityRate, na.rm=TRUE)),
                       labels = c('Minimum','','','','','','Maximum'))+

  theme_bw()+
  ggtitle("b) Respiratory Mortality Rates Per 100K")+
  theme(legend.position = 'none')+
  theme(legend.spacing.y = unit(.5,'cm'),
        legend.text = element_text(size=12),
        legend.title = element_text(size=13))+
  theme(plot.title = element_text(size = 20))+
  guides(col = guide_legend(override.aes = list(shape = 15, size = 10)))+
  theme(panel.border = element_rect(color = "transparent"),
        axis.text.x= element_blank(),
        axis.ticks.x = element_blank())
p6

#population
p7 <- ggplot() +
  geom_sf(data = MergedData, color = "black",  aes(fill = mean_pop))+
  coord_sf(crs = "+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 
           +datum=WGS84 +units=m +no_defs")+
  scale_fill_fermenter("Population",
                       n.breaks=9,
                        type = 'seq',
                       direction = -1,
                        palette = "Spectral",
                        na.value='lightgray',
                       limits=c(min(MergedData$mean_pop, na.rm=TRUE),
                                max(MergedData$mean_pop, na.rm=TRUE)),
                       #breaks= c(0,100,1000,5000,10000,20000,40000,60000,100000),
                       #breaks= c(0,100,1000,10000,100000),
                       #n.breaks = 6,
                       #label=scales::comma)+
                       labels = c('Minimum','','','','','','Maximum'))+
  theme_bw()+
  ggtitle('a) Population')+
  theme(legend.position = 'none')+
  theme(legend.spacing.y = unit(.5,'cm'),
        legend.text = element_text(size=12),
        legend.title = element_text(size=13))+
  theme(plot.title = element_text(size = 20))+
  guides(col = guide_legend(override.aes = list(shape = 15, size = 10)))+
  theme(panel.border = element_rect(color = "transparent"),
        axis.text.x= element_blank(),
        axis.ticks.x = element_blank())
p7

#avg response
p8 <- ggplot() +
  geom_sf(data = MergedData, color = "black",  aes(fill = AvgResponse))+
  coord_sf(crs = "+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 
           +datum=WGS84 +units=m +no_defs")+
  scale_fill_fermenter("",
                       n.breaks=9,
                        type = 'seq',
                       direction = -1,
                        palette = "Spectral",
                        na.value='lightgray',
                       limits=c(min(MergedData$AvgResponse, na.rm=TRUE),
                                max(MergedData$AvgResponse, na.rm=TRUE)),
                       labels = c('Minimum','','','','','','Maximum'))+
  theme_bw()+
  ggtitle(expression(paste('c) Average Ozone Response (pptv ', O[3],"/", "ppbv ",CH[4],')')))+
  theme(legend.position = 'bottom')+
  theme(legend.key.width = unit(2,'cm'),
        legend.text = element_text(size=12),
        legend.title = element_text(size=13))+
  theme(plot.title = element_text(size = 20))+
  theme(panel.border = element_rect(color = "transparent"),
        axis.text.x= element_blank(),
        axis.ticks.x = element_blank())
p8

@@

Plots <- file.path('../..','analysis','Manuscript','Plots')
inputs <- file.path('../..','analysis','Manuscript','BenMAP','Outputs')
countryresults <-
   read_csv(file.path(inputs,"npd_country_damage_transformation_woutCessation.csv"),
           col_types = cols())

@@

## function for labels
means = cResultslong %>% 
  group_by_at(c('discount.rate','SuperRegion')) %>% 
  summarise(means=mean) %>% 
  ungroup() %>%
  #mutate(across(c('means'), ~ signif(.,3))) %>%
  mutate(means = case_when( means >100 ~ signif(means,2), TRUE ~signif(means,1)))

lower = cResultslong %>% 
  group_by_at(c('discount.rate','SuperRegion')) %>% 
  summarise(means=`2.5%`) %>% 
  ungroup() %>%
  mutate(across(c('means'), ~ signif(.,2)))

upper = cResultslong %>% 
  group_by_at(c('discount.rate','SuperRegion')) %>% 
  summarise(means=`97.5%`) %>% 
  ungroup() %>%
  mutate(across(c('means'), ~ signif(.,2)))

@@

#Read in 
Plots <- file.path('../..', 'analysis','Manuscript','Plots')
inputs <- file.path('../..','analysis','Manuscript','BenMAP','Outputs')
rft_inputs <- file.path('../..','output','npd')

@@

p1 <- plot_data %>%
  mutate(subgroup_col = (fct_relevel(subgroup_col, '3.0% CDR',
                                     "2.0% CDR","3.0% Ramsey",
                                     "2.5% Ramsey","1.5% Ramsey",
                                     "MIROC","GISS","GFDL",
                                     "CESM2","HadGEM",
                                     '-50% NOx','+50% NOx',
                                     "SocioEcon. Lower","SocioEcon. Upper",
                                     "CRF Lower","CRF Upper"
                                     ))) %>%
  ggplot( aes(x=(subgroup_col), y=(val_col),fill=group_col))+
  geom_bar(stat='identity',width = 0.4)+
  #scale_fill_brewer() (palette = 'Spectral',direction=-1)+
  scale_fill_manual(name = '',values=c(brewer.pal(11,"Spectral")[c(2,4,8,10,11)]),
  breaks= c('CRF (95% CI)','Socioeconomics (95% CI)','NOx Emissions (\u0394 50%)','GCM (mean)','Discount Rate (mean)'))+
  coord_flip()+
  theme_minimal()+
  xlab('')+
  ylab("Change in Global $1700(2020)/mT" ~CH[4])+
  theme(axis.text = element_text(size=16),
        axis.title = element_text(size=16))+
  scale_y_continuous(limits = c(-1000, 1300),label = scales::dollar)+
  theme(legend.position = c(0.8,0.25),
        legend.title=element_text(size=14), 
        legend.text=element_text(size=14))
